MCC Kids Model Predictions

### 2018-11-28 stats/kids/kids_model_predictions.Rmd
sketch out full bda model

>>>>

## MH sketching

```{r}
postPrefConWebppl <- '

var levels = function(df, label){
  return _.uniq(_.map(df, label));
}
var prefData = filter(dataFromR, {experiment: "preference"})
var infData = filter(dataFromR, {experiment: "informativeness"})

// make finer grained as needed
var binned_age_range = _.range(0, 2, 0.1)

var all_conditions = levels(prefData, "condition")

var priorProbs = []

    var speakerOptimality = so_int  + so_slope * (age - infData[0].minage)
    var inf_priorProbs = [.5, .5, .5]

    var rsaPredictions = pragmaticListener({label: "dax", point: 2 },
    inf_priorProbs, speakerOptimality)

  var pref_params = map(function(cndtn){
    var conditionData = filter(prefData, {condition: cndtn})

    }, conditionData)

    return {pref_int, pref_slope, condition: cndtn}

  }, all_conditions)

  var diff_speaker_params = filter(pref_params, 
        {condition: "different_speaker"})[0]

  var same_speaker_params = filter(pref_params, 
        {condition: "same_speaker"})[0]

  var predictions_by_age = map(function(age_bin){

    var speakerOptimality = so_int  + so_slope * age_bin

    var diff_priorReg = logistic(diff_speaker_params.pref_int +
            diff_speaker_params.pref_slope * age_bin)

    var diff_priorProbs_congruent = [1-priorReg, 1-priorReg, priorReg]
    var diff_priorProbs_incongruent = [priorReg, priorReg, 1-priorReg]

  var rsaPredictions_diff_cong = expectation(pragmaticListener({label: "dax", point: 2 }, diff_priorProbs_congruent, speakerOptimality))

      ...

    var same_priorReg = logistic(same_speaker_params.pref_int +
            same_speaker_params.pref_slope * age_bin)

    ...

    return extend(diff_speaker_params, same_speaker_params, {
      diff_priorReg,
      same_priorReg,
      speakerOptimality,
      rsaPredictions_diff_cong,
      rsaPredictions_diff_incong,
      rsaPredictions_same_cong,
      rsaPredictions_same_incong,
      age_bin,
      so_slope,
      so_int
    })

  }, binned_age_range)

  return predictions_by_age
}
'
```

```{r}
postSoWebppl <- '
